Developing a Visual Studio Code Language Support Extension for the Snail Programming Language

### 2023-07-08 paper.tex
chore: sorted and fixed bibliography
backup
feat: highlight appendix code

\colorlet{punct}{red!60!black}
\definecolor{background}{HTML}{EEEEEE}
\definecolor{delim}{RGB}{20,105,176}
\colorlet{numb}{magenta!60!black}

@@

\definecolor{lightgray}{rgb}{.9,.9,.9}
\definecolor{darkgray}{rgb}{.4,.4,.4}
\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
\lstdefinelanguage{OldTypeScript}{
  keywords={abstract, any, as, boolean, break, case, catch, class, console, const, continue, debugger, declare, default, delete, do, else, enum, export, extends, false, finally, for, from, function, get, if, implements, import, in, infer, instanceof, interface, keyof, let, module, namespace, never, new, null, number, object, package, private, protected, public, readonly, require, return, set, static, string, super, switch, symbol, this, throw, true, try, type, typeof, undefined, unique, unknown, var, void, while, with, yield},
  morecomment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]',
  morestring=[b]",
  ndkeywords={class, export, boolean, throw, implements, import, this},
  keywordstyle=\color{blue}\bfseries,
  ndkeywordstyle=\color{darkgray}\bfseries,
  identifierstyle=\color{black},
  commentstyle=\color{purple}\ttfamily,
  stringstyle=\color{red}\ttfamily,
  sensitive=true,
  backgroundcolor=\color{lightgray},
  extendedchars=true,
  basicstyle=\ttfamily,
  showstringspaces=false,
  showspaces=false,
  numbers=left,
  numberstyle=,
  numbersep=9pt,
  tabsize=2,
  breaklines=true,
  showtabs=false,
  captionpos=b
}

\colorlet{comment}{green}
\lstdefinelanguage{TypeScript}{
    basicstyle=\normalfont\ttfamily,
    numbers=left,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    frame=lines,
    backgroundcolor=\color{background},
    literate=
     *{0}{{{\color{numb}0}}}{1}
      {1}{{{\color{numb}1}}}{1}
      {2}{{{\color{numb}2}}}{1}
      {3}{{{\color{numb}3}}}{1}
      {4}{{{\color{numb}4}}}{1}
      {5}{{{\color{numb}5}}}{1}
      {6}{{{\color{numb}6}}}{1}
      {7}{{{\color{numb}7}}}{1}
      {8}{{{\color{numb}8}}}{1}
      {9}{{{\color{numb}9}}}{1}
      {:}{{{\color{punct}{:}}}}{1}
      {,}{{{\color{punct}{,}}}}{1}
      {\{}{{{\color{delim}{\{}}}}{1}
      {\}}{{{\color{delim}{\}}}}}{1}
      {[}{{{\color{delim}{[}}}}{1}
      {]}{{{\color{delim}{]}}}}{1},
    morecomment=[l]{//},
    morecomment=[s]{/*}{*/},
    commentstyle=\color{green}\ttfamily
}

\graphicspath{ {./images/} }

@@

\bibliography{refs.bib}
\bibliographystyle{plain}

@@

    The following is the \lstinline{snaildap.re} file from the snail language interpreter, which defines the snail-level debug adapter used to respond to debug adapter protocol requests.
    \lstinputlisting[]{
        /Users/charlesreinhardt/Git/snail/src/snaildap.re
    }
    \label{app:snaildap}

>>>>

\definecolor{darkred}{HTML}{690101}
\definecolor{lightgray}{HTML}{EEEEEE}
\definecolor{lightblue}{HTML}{146ab0}
\definecolor{lightpurple}{HTML}{a555ab}

\colorlet{punct}{darkred}
\colorlet{background}{lightgray}
\colorlet{delim}{lightblue}
\colorlet{numb}{lightpurple}

@@

\definecolor{green}{HTML}{2d6e21}
\definecolor{red}{HTML}{d41313}
\definecolor{blue}{HTML}{1323d4}
\definecolor{purple}{HTML}{7d13d4}

\colorlet{comment}{green}
\colorlet{string}{red}
\colorlet{keyword1}{blue}
\colorlet{keyword2}{purple}

\lstdefinelanguage{TypeScript}{
    basicstyle=\normalfont\ttfamily,
    numbers=left,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    frame=lines,
    backgroundcolor=\color{background},
    literate=
     *{0}{{{\color{numb}0}}}{1}
      {1}{{{\color{numb}1}}}{1}
      {2}{{{\color{numb}2}}}{1}
      {3}{{{\color{numb}3}}}{1}
      {4}{{{\color{numb}4}}}{1}
      {5}{{{\color{numb}5}}}{1}
      {6}{{{\color{numb}6}}}{1}
      {7}{{{\color{numb}7}}}{1}
      {8}{{{\color{numb}8}}}{1}
      {9}{{{\color{numb}9}}}{1}
      {:}{{{\color{punct}{:}}}}{1}
      {,}{{{\color{punct}{,}}}}{1}
      {;}{{{\color{punct}{;}}}}{1}
      {\{}{{{\color{delim}{\{}}}}{1}
      {\}}{{{\color{delim}{\}}}}}{1}
      {[}{{{\color{delim}{[}}}}{1}  
      {]}{{{\color{delim}{]}}}}{1},
    morecomment=[l]{//},
    morecomment=[s]{/*}{*/},
    commentstyle=\color{comment}\ttfamily,
    morestring=[b]',
    morestring=[b]",
    stringstyle=\color{string}\ttfamily,
    keywords={if, else, import, as, from, return, await, try, catch, throw, finally, number, string, true, false, undefined, new},
    otherkeywords={=>},
    keywordstyle=\color{keyword1},
    keywords=[3]{const, let, interface, function, async},
    keywordstyle=[3]\color{keyword2},
}

\lstdefinelanguage{Reason}{
    basicstyle=\normalfont\ttfamily,
    numbers=left,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    frame=lines,
    backgroundcolor=\color{background},
    literate=
     *{0}{{{\color{numb}0}}}{1}
      {1}{{{\color{numb}1}}}{1}
      {2}{{{\color{numb}2}}}{1}
      {3}{{{\color{numb}3}}}{1}
      {4}{{{\color{numb}4}}}{1}
      {5}{{{\color{numb}5}}}{1}
      {6}{{{\color{numb}6}}}{1}
      {7}{{{\color{numb}7}}}{1}
      {8}{{{\color{numb}8}}}{1}
      {9}{{{\color{numb}9}}}{1}
      {:}{{{\color{punct}{:}}}}{1}
      {,}{{{\color{punct}{,}}}}{1}
      {;}{{{\color{punct}{;}}}}{1}
      {\{}{{{\color{delim}{\{}}}}{1}
      {\}}{{{\color{delim}{\}}}}}{1}
      {[}{{{\color{delim}{[}}}}{1}  
      {]}{{{\color{delim}{]}}}}{1},
    morecomment=[l]{//},
    morecomment=[s]{/*}{*/},
    commentstyle=\color{comment}\ttfamily,
    morestring=[b]',
    morestring=[b]",
    stringstyle=\color{string}\ttfamily,
    keywords={open, ref, try},
    otherkeywords={=>, \%},
    keywordstyle=\color{keyword1},
    keywords=[3]{let, module, program},
    keywordstyle=[3]\color{keyword2}
}

\graphicspath{ {./images} }

@@

\bibliography{refs.bib}
\bibliographystyle{acm}

@@

    The following is the \lstinline{snaildap.re} file from the snail language interpreter, which defines the snail-level debug adapter used to respond to debug adapter protocol requests.
    \lstinputlisting[language=Reason]{
        /Users/charlesreinhardt/Git/snail/src/snaildap.re
    }
    \label{app:snaildap}
